---
title: "Kanamycin_Network"
author: "N Billows"
date: "05/09/2023"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This R Markdown document is made interactive using Shiny. Unlike the more traditional workflow of creating static reports, you can now create documents that allow your readers to change the assumptions underlying your analysis and see the results immediately. 

To learn more, see [Interactive Documents](http://rmarkdown.rstudio.com/authoring_shiny.html).

## Inputs and Outputs

You can embed Shiny inputs and outputs in your document. Outputs are automatically updated whenever inputs change.  This demonstrates how a standard R plot can be made interactive by wrapping it in the Shiny `renderPlot` function. The `selectInput` and `sliderInput` functions create the input widgets used to drive the plot.

```{r eruptions, echo=FALSE}
library(dplyr)
library(visNetwork)
library(shiny)

#### PARAMS ####
genes_of_interest <- c("rrs", "eis")
genes_of_interest_known <-c("rrs", "eis")
genes_of_interest_compensatory <- c("X")
drug_name <- c("kanamycin")
all_drug_names <- c("kanamycin")
thresholds_hl <-2
thresholds_ul <-0
thresholds_u <- 1.5

cand_gene <- c("embR","rrs", "fabG1","inhA","rpsA","tlyA","katG","pncA","kasA","panD","embC","embA","embB",NA,"gid", "gyrB","gyrA","rpoB","rpoC","rpsL","ahpC","eis" )

hgvs <- read.csv("~/phd/Data/Chapter3/Annotation/hgvs.csv")

hgvs <- hgvs %>%   filter(Effect=="MODIFIER" & Gene %in% c("rrs")|!Effect=="MODIFIER" & !Gene  %in% c("rrs"))
hgvs[is.na(hgvs[,c("Protein_Change")]),c("Protein_Change")]  <- hgvs[is.na(hgvs[,c("Protein_Change")]),c("NA_Change")]  
hgvs$ID <- paste0(hgvs$ID,"_",hgvs$Position,"_",hgvs$Alt_Allele)
hgvs <- unique(hgvs)
##### Lineage
lineage_snp_id <- read.csv("~/phd/Data/RFnetworks/lineage_snp_id.csv", sep="")
lineage_barcode <- read.csv("~/phd/Data/RFnetworks/lineage_barcode.csv")
lineage_barcode$id <- paste0("Chromosome_",lineage_barcode$Pos,"_",lineage_barcode$Alt)

interactions2 <- read.csv(paste0("~/phd/Data/RFnetworks/",drug_name,"_interactions2.csv"))
interactions2 <- interactions2[,-1]
interactions2 <- data.frame(apply(interactions2, 2, function(x) gsub(" ", "", x)))
interactions2 <- unique(interactions2)
interactions2 <- left_join(interactions2, hgvs, by= c("Mutation_1"="ID"))
interactions2 <- left_join(interactions2, hgvs, by= c("Mutation_2" = "ID"))
interactions2[grepl("fs", interactions2$Protein_Change.x),c("Protein_Change.x")] <- interactions2[grepl("fs", interactions2$Protein_Change.x),c("NA_Change.x")]
interactions2[grepl("fs", interactions2$Protein_Change.y),c("Protein_Change.y")] <- interactions2[grepl("fs", interactions2$Protein_Change.y),c("NA_Change.y")]
########NEED TO ESCAPE ????
interactions2[grepl("\\?", interactions2$Protein_Change.x),c("Protein_Change.x")] <- interactions2[grepl("\\?", interactions2$Protein_Change.x),c("NA_Change.x")]
interactions2[grepl("\\?", interactions2$Protein_Change.y),c("Protein_Change.y")] <- interactions2[grepl("\\?", interactions2$Protein_Change.y),c("NA_Change.y")]


interactions2 <- interactions2 %>% filter(Gene.x %in% cand_gene & Gene.y %in% cand_gene)



tbdb <- read.csv("~/phd/Data/Chapter3/Annotation/tbdb.csv")
interactions2$known_1 <- NA
interactions2$coocurring_1 <- NA
interactions2$known_2 <- NA
interactions2$coocurring_2 <- NA
interactions2$total_effect1 <- NA
interactions2$total_effect2 <- NA
interactions2$candgene1 <- NA
interactions2$candgene2 <- NA
known<- tbdb %>% filter(Drug==paste0(drug_name))
coocurring <- tbdb %>% filter(!Drug %in% all_drug_names)
interactions2$known_1 <- ifelse(interactions2$Protein_Change.x %in% known$Mutation & interactions2$Gene.x %in% c(genes_of_interest), 1,0)
interactions2$known_2 <- ifelse(interactions2$Protein_Change.y %in% known$Mutation & interactions2$Gene.y %in% c(genes_of_interest), 1,0)
interactions2$coocurring_1 <- ifelse(interactions2$Protein_Change.x %in% coocurring$Mutation & !interactions2$Gene.x %in% c(genes_of_interest), 1,0)
interactions2$coocurring_2 <- ifelse(interactions2$Protein_Change.y %in% coocurring$Mutation & !interactions2$Gene.y %in% c(genes_of_interest), 1,0)
interactions2$lineage_1 <- ifelse(interactions2$Mutation_1 %in% lineage_barcode$id, 1,0)
interactions2$lineage_2 <- ifelse(interactions2$Mutation_2 %in% lineage_barcode$id, 1,0)
interactions2$total_effect1 <- ifelse(interactions2$Effect.x %in% c("HIGH", "MODERATE"), 1,0)
interactions2$total_effect2<- ifelse(interactions2$Effect.y %in% c("HIGH", "MODERATE"), 1,0)
interactions2$candgene1 <- ifelse(interactions2$Gene.x %in% c(genes_of_interest), 1,0)
interactions2$candgene2<- ifelse(interactions2$Gene.y %in% c(genes_of_interest), 1,0)
interactions2$score_1 <- NA
interactions2[,25:32] <- apply(interactions2[,25:32],2, function(x) as.numeric(as.character(x)))
interactions2 <- data.frame(interactions2)
interactions2$score_1 <-  interactions2$known_1 + interactions2$known_2 - interactions2$coocurring_1 - interactions2$coocurring_2 + interactions2$total_effect1 + interactions2$total_effect2 + interactions2$candgene1 + interactions2$candgene2 - interactions2$lineage_1 - interactions2$lineage_2
interactions2$score_2 <- interactions2$score_1 * as.numeric(as.character(interactions2$coeff))
interactions2$ks_1 <- NA
for (i in 1: nrow(interactions2)){
  if (interactions2$score_2[i]>=thresholds_hl){
    interactions2$ks_1[i] <- "Highly likely"
  }
  if (interactions2$score_2[i]<=thresholds_ul){
    interactions2$ks_1[i] <- "Highly unlikely"
  }
  if (interactions2$score_2[i]>thresholds_ul & interactions2$score_2[i]<thresholds_u){
    interactions2$ks_1[i] <- "Unlikely"
  }
  if (interactions2$score_2[i]>=thresholds_u & interactions2$score_2[i]<thresholds_hl){
    interactions2$ks_1[i] <- "Likely"
  }
}
interactions2$ec_1 <- "grey"
interactions2$ec_2 <- "black"

interactions2$gen_int <- 1
interactions2$ks_2 <- interactions2$ks_1
interactions2$name.x <- paste0(interactions2$Gene.x,": ",interactions2$Protein_Change.x)
interactions2$name.y <- paste0(interactions2$Gene.y,": ",interactions2$Protein_Change.y)
network_df <- interactions2 %>% filter(score_1>5)

string_interactions_short <- read.delim("~/phd/Data/RFnetworks/string_interactions_short.tsv", header=FALSE, comment.char="#")
string_interactions_short <- string_interactions_short[,c(1:2,13)]
colnames(string_interactions_short) <- c("P1", "P2", "coeff")
string_interactions_short$candgene1 <- ifelse(string_interactions_short$P1 %in% c(genes_of_interest), 1,0)
string_interactions_short$candgene2<- ifelse(string_interactions_short$P2 %in% c(genes_of_interest), 1,0)
string_interactions_short$known_1 <- ifelse(string_interactions_short$P1 %in% c(genes_of_interest), 1,0)
string_interactions_short$known_2<- ifelse(string_interactions_short$P2 %in% c(genes_of_interest), 1,0)
string_interactions_short$coocurring_1 <- ifelse(string_interactions_short$P1 %in% c(genes_of_interest), 0,1)
string_interactions_short$coocurring_2<- ifelse(string_interactions_short$P2 %in% c(genes_of_interest), 0,1)
string_interactions_short$ks_1 <- "Not Applicable"
string_interactions_short <- unique(string_interactions_short)
string_interactions_short$name.x <- string_interactions_short$P1
string_interactions_short$name.y <- string_interactions_short$P2
string_interactions_short$ec_1 <- "black"
string_interactions_short$group_1 <- paste0(string_interactions_short$P1,"_PPI")
string_interactions_short$group_2 <- paste0(string_interactions_short$P2,"_PPI")



## Let's make nodes data.frame
nodes <- data.frame(id=c(interactions2$Mutation_1, interactions2$Mutation_2, string_interactions_short$P1, string_interactions_short$P2),  
                    gene = c(interactions2$Gene.x, interactions2$Gene.y, string_interactions_short$P1, string_interactions_short$P2), 
                    candgene= c(interactions2$candgene1, interactions2$candgene2, string_interactions_short$candgene1, string_interactions_short$candgene2), 
                    known= c(interactions2$known_1, interactions2$known_2, string_interactions_short$known_1, string_interactions_short$known_2), 
                    coocurring=c(interactions2$coocurring_1, interactions2$coocurring_2, string_interactions_short$coocurring_1, string_interactions_short$coocurring_2),
                    name= c(interactions2$name.x, interactions2$name.y, string_interactions_short$name.x, string_interactions_short$name.y),
                    group=c(interactions2$Gene.x, interactions2$Gene.y, string_interactions_short$group_1, string_interactions_short$group_2))
nodes <- unique(nodes)
nodes$title <- paste0("<p><b>", nodes$name,"</b><br> </p>")
nodes$type <- NA
for (i in 1: nrow(nodes)){
  if (nodes$id[i] %in% c(genes_of_interest_known)){
    nodes$type[i] <- "Known"
  }
  if (nodes$id[i] %in% c(genes_of_interest_compensatory)){
    nodes$type[i] <- "Compensatory"
  }
  if (!nodes$id[i] %in% c(genes_of_interest)){
    nodes$type[i] <- "Co-occurring"
  }
  if (nodes$known[i]>0){
    if (nodes$gene[i] %in% c(genes_of_interest_compensatory)){
      nodes$type[i] <- "Compensatory"
    } else {
      nodes$type[i] <- "Known"
    }
  }
  if (nodes$coocurring[i]>0){
    nodes$type[i] <- "Co-occurring"
  }
  if (nodes$known[i]<1 & nodes$coocurring[i]<1){
    if (nodes$id[i] %in% lineage_barcode$id){
      nodes$type[i] <- "Lineage"
    } else {
      nodes$type[i] <- "Other"
    }
  }
}
nodes$candgene2 <- NA
nodes$candgene2 <- ifelse(nodes$candgene>0, "Yes", "No")
nodes$shape <- NA
nodes$shadow <- NA
nodes$border <- NA
nodes$size <- NA
nodes$label <- NA
nodes$value <- NA
for (i in 1:nrow(nodes)){
  if(nodes$id[i] %in% unique(nodes$gene)){
    nodes$shape[i]<- "ellipse"
    nodes$shadow[i]<- TRUE
    nodes$border[i]<- "black"
    nodes$value[i]<- 50000
    nodes$size[i]<- 100
    nodes$label[i]<- nodes$id[i]
  } else {
    nodes$shape[i]<- "dot"
    nodes$shadow[i]<- FALSE
    nodes$label[i]<- nodes$name[i]
    nodes$size[i]<- 50
  }
  
  
  
}




interactions2$width1 <- 0.2
interactions2$width2 <- 0.2
interactions2$dash1<- FALSE
interactions2$dash2 <- TRUE
string_interactions_short$width1 <- 0.2
string_interactions_short$ec_1 <- "black"
string_interactions_short$dash <- TRUE
edges <- data.frame(from = c(interactions2$Mutation_1,interactions2$Mutation_1, interactions2$Mutation_2, string_interactions_short$P1), 
                    to = c(interactions2$Mutation_2, interactions2$Gene.x, interactions2$Gene.y, string_interactions_short$P2), 
                    knowledge_score = c(interactions2$ks_1, interactions2$ks_2, interactions2$ks_2, string_interactions_short$ks_1), 
                    coeff= c(interactions2$coeff, interactions2$gen_int, interactions2$gen_int, string_interactions_short$coeff),
                    edge_colour= c(interactions2$ec_1, interactions2$ec_2, interactions2$ec_2, string_interactions_short$ec_1),
                    value= c(interactions2$width1, interactions2$width2,interactions2$width2, string_interactions_short$width1),
                    dashes=c(interactions2$dash1, interactions2$dash2, interactions2$dash2,string_interactions_short$dash))

edges$name <- paste0(edges$to,"_",edges$from)

edges$coeff2 <- NA
edges$coeff2 <- ifelse(edges$coeff>=0.7, "Yes", "No")

#edges$dashes <- TRUE
edges$value <- NULL

edges <- unique(edges)


ui <- fluidPage(title = "example",
                fillPage(sidebarLayout(
                  sidebarPanel(
                    selectInput(
                      inputId = "filterNodes",
                      label = "Filter nodes in candidate genes:",
                      choices = c("Yes", "No"),
                      selected = c("No")
                    ), 
                    checkboxGroupInput(
                      inputId = "filterEdges",
                      label = paste0("Role in ", drug_name, " resistance:"),
                      choices = unique(edges$knowledge_score),
                      selected = unique(edges$knowledge_score)
                    )
                    ,
                    selectInput(
                      inputId = "filterEdges2",
                      label = "Show strong interactions only:",
                      choices = c("Yes", "No"),
                      selected = c("No")
                    ),
                    checkboxGroupInput(
                      inputId = "filterNodes2",
                      label = "Confers:",
                      choices = unique(nodes$type),
                      selected = unique(nodes$type)
                    ),
                    selectInput(
                      inputId = "filterNodes3",
                      label = "Hide PPI network:",
                      choices = c("Yes", "No"),
                      selected = c("No")
                    ),
                    selectInput(
                      inputId = "layout",
                      label = "Layout:",
                      choices = c("Default", "Circle"),
                      selected = c("Default")
                    )
                    ,
                    width = 3
                  ),
                  mainPanel(
                    visNetworkOutput("network_proxy_update", width = "100%", height = "90vh"),  
                    width = 9
                  )
                )))
ui <- fluidPage(title = "example",
                fillPage(sidebarLayout(
                  sidebarPanel(
                    selectInput(
                      inputId = "filterNodes",
                      label = "Filter nodes in candidate genes:",
                      choices = c("Yes", "No"),
                      selected = c("Yes")
                    ), 
                    checkboxGroupInput(
                      inputId = "filterEdges",
                      label = paste0("Role in ", drug_name, " resistance:"),
                      choices = unique(edges$knowledge_score),
                      selected = c("Likely", "Highly likely", "Not Applicable")
                    )
                    ,
                    selectInput(
                      inputId = "filterEdges2",
                      label = "Show strong interactions only:",
                      choices = c("Yes", "No"),
                      selected = c("No")
                    ),
                    checkboxGroupInput(
                      inputId = "filterNodes2",
                      label = "Confers:",
                      choices = unique(nodes$type),
                      selected = unique(nodes$type)
                    ),
                    selectInput(
                      inputId = "filterNodes3",
                      label = "Hide PPI network:",
                      choices = c("Yes", "No"),
                      selected = c("No")
                    ),
                    selectInput(
                      inputId = "layout",
                      label = "Layout:",
                      choices = c("Default", "Circle"),
                      selected = c("Default")
                    )
                    ,
                    width = 3
                  ),
                  mainPanel(
                    visNetworkOutput("network_proxy_update", width = "100%", height = "90vh"),  
                    width = 9
                  )
                )))


nodes$font.size <- 30

server <- function(input, output) {
  output$network_proxy_update <- renderVisNetwork({
    visNetwork(nodes, edges) %>%  visIgraphLayout(randomSeed = 10) %>%
      visGroups(groupname = "rpoB", color = "#56B4E9") %>%
      visGroups(groupname = "rpoC", color = "#0072B2") %>%
      
      visGroups(groupname = "katG", color = "#D55E00") %>%
      visGroups(groupname = "inhA", color = "#E69F00") %>%
      visGroups(groupname = "ahpC", color = "#f2bf4e") %>%
      visGroups(groupname = "kasA", color = "#ebc97f") %>%
      visGroups(groupname = "fabG1", color = "#edd59f") %>%
      
      visGroups(groupname = "embA", color = "#4da890") %>%
      visGroups(groupname = "embB", color = "#009E73") %>%
      visGroups(groupname = "embC", color = "#68ab99") %>%
      visGroups(groupname = "embR", color = "#84ada2") %>%
      
      visGroups(groupname = "panD", color = "#F0E442") %>%
      visGroups(groupname = "pncA", color = "#f0e662") %>%
      visGroups(groupname = "rpsA", color = "#f0e884") %>%
      
      visGroups(groupname = "gid", color = "#CC79A7") %>%
      visGroups(groupname = "rpsL", color = "#cc8baf") %>%
      visGroups(groupname = "rrs", color = "#c9a1b7") %>%
      visGroups(groupname = "tlyA", color = "#c9bbc3") %>%
      visGroups(groupname = "eis", color = "#c9c9c9") %>%
      
      visGroups(groupname = "gyrA", color = "#999999") %>%
      visGroups(groupname = "gyrB", color = "#7d7d7d") %>%
      
      visGroups(groupname = "rpoB_PPI", color =  "#56B4E9") %>%
      visGroups(groupname = "rpoC_PPI", color =  "#0072B2") %>%
      
      visGroups(groupname = "katG_PPI", color =  "#D55E00") %>%
      visGroups(groupname = "inhA_PPI", color =  "#E69F00") %>%
      visGroups(groupname = "ahpC_PPI", color =  "#f2bf4e") %>%
      visGroups(groupname = "kasA_PPI", color =  "#ebc97f") %>%
      visGroups(groupname = "fabG1_PPI", color =  "#edd59f") %>%
      
      visGroups(groupname = "embA_PPI", color =  "#4da890") %>%
      visGroups(groupname = "embB_PPI", color =  "#009E73") %>%
      visGroups(groupname = "embC_PPI", color =  "#68ab99") %>%
      visGroups(groupname = "embR_PPI", color =  "#84ada2") %>%
      
      visGroups(groupname = "panD_PPI", color =  "#F0E442") %>%
      visGroups(groupname = "pncA_PPI", color =  "#f0e662") %>%
      visGroups(groupname = "rpsA_PPI", color =  "#f0e884") %>%
      
      visGroups(groupname = "gid_PPI", color =  "#CC79A7") %>%
      visGroups(groupname = "rpsL_PPI", color =  "#cc8baf") %>%
      visGroups(groupname = "rrs_PPI", color =  "#c9a1b7") %>%
      visGroups(groupname = "tlyA_PPI", color =  "#c9bbc3") %>%
      visGroups(groupname = "eis_PPI", color =  "#c9c9c9") %>%
      
      visGroups(groupname = "gyrA_PPI", color =  "#999999") %>%
      visGroups(groupname = "gyrB_PPI", color =  "#7d7d7d") %>%
      
      visLegend(addNodes = list(list(label="rpoB",shape="dot",size=10,color="#56B4E9",font=list(color="black", size=10)),
                                list(label="rpoC",shape="dot",size=10,color="#0072B2",font=list(color="black", size=10)),
                                list(label="katG",shape="dot",size=10,color="#D55E00",font=list(color="black", size=10)),
                                list(label="inhA",shape="dot",size=10,color="#E69F00",font=list(color="black", size=10)),
                                list(label="ahpC",shape="dot",size=10,color="#f2bf4e",font=list(color="black", size=10)),
                                list(label="kasA",shape="dot",size=10,color="#ebc97f",font=list(color="black", size=10)),
                                list(label="fabG1",shape="dot",size=10,color="#edd59f",font=list(color="black", size=10)),
                                list(label="embA",shape="dot",size=10,color="#4da890",font=list(color="black", size=10)),
                                list(label="embB",shape="dot",size=10,color="#009E73",font=list(color="black", size=10)),
                                list(label="embC",shape="dot",size=10,color="#68ab99",font=list(color="black", size=10)),
                                list(label="embR",shape="dot",size=10,color="#84ada2",font=list(color="black", size=10)),
                                list(label="panD",shape="dot",size=10,color="#F0E442",font=list(color="black", size=10)),
                                list(label="pncA",shape="dot",size=10,color="#f0e662",font=list(color="black", size=10)),
                                list(label="rpsA",shape="dot",size=10,color="#f0e884",font=list(color="black", size=10)),
                                list(label="gid",shape="dot",size=10,color="#CC79A7",font=list(color="black", size=10)),
                                list(label="rpsL",shape="dot",size=10,color="#cc8baf",font=list(color="black", size=10)),
                                list(label="rrs",shape="dot",size=10,color="#c9a1b7",font=list(color="black", size=10)),
                                list(label="tlyA",shape="dot",size=10,color="#c9bbc3",font=list(color="black", size=10)),
                                list(label="eis",shape="dot",size=10,color="#c9c9c9",font=list(color="black", size=10)),
                                list(label="gyrA",shape="dot",size=10,color="#999999",font=list(color="black", size=10)),
                                list(label="gyrB",shape="dot",size=10,color="#7d7d7d",font=list(color="black", size=10)))
                ,
                useGroups = FALSE, ncol=3) %>% 
      visNodes(font = list(size = 25) , 
               scaling = list(label = list(
                 enabled = TRUE, 
                 min = 25, max = 100, 
                 maxVisible = 100, 
                 drawThreshold = 1
               )))
  })
  myVisNetworkProxy <- visNetworkProxy("network_proxy_update") 
  observe ({
    myfilteredEdges <- edges %>% filter(knowledge_score %in% input$filterEdges) %>% filter(if ("Yes" %in% input$filterEdges2){
      coeff2 %in% c("Yes")
    } else {
      coeff2 %in% unique(coeff2) 
    })                                                                                    
    
    myfilteredNodes <- nodes %>% filter(if ("Yes" %in% input$filterNodes){
      candgene %in% c(1)
    } else {
      candgene %in% c(0,1)      
    }) %>% 
      filter(id %in% c(myfilteredEdges$to, myfilteredEdges$from)) %>% filter(type %in% input$filterNodes2)  %>% 
      filter(if ("Yes" %in% input$filterNodes3){
        !id %in% unique(nodes$gene)
      } else {
        id %in% id
      })
    myhiddenEdges <- anti_join(edges, myfilteredEdges)
    myhiddenNodes <- anti_join(nodes, myfilteredNodes)
    visRemoveEdges(myVisNetworkProxy, id = myhiddenEdges$name)
    visRemoveNodes(myVisNetworkProxy, id = myhiddenNodes$id)
    visUpdateEdges(myVisNetworkProxy, myfilteredEdges)
    visUpdateNodes(myVisNetworkProxy, nodes = myfilteredNodes)
    if (nrow(myfilteredNodes)<200){
      output$network_proxy_update <- renderVisNetwork({
        plot1 <- visNetwork(myfilteredNodes, myfilteredEdges) %>%  
          visGroups(groupname = "rpoB", color = "#56B4E9") %>%
          visGroups(groupname = "rpoC", color = "#0072B2") %>%
          
          visGroups(groupname = "katG", color = "#D55E00") %>%
          visGroups(groupname = "inhA", color = "#E69F00") %>%
          visGroups(groupname = "ahpC", color = "#f2bf4e") %>%
          visGroups(groupname = "kasA", color = "#ebc97f") %>%
          visGroups(groupname = "fabG1", color = "#edd59f") %>%
          
          visGroups(groupname = "embA", color = "#4da890") %>%
          visGroups(groupname = "embB", color = "#009E73") %>%
          visGroups(groupname = "embC", color = "#68ab99") %>%
          visGroups(groupname = "embR", color = "#84ada2") %>%
          
          visGroups(groupname = "panD", color = "#F0E442") %>%
          visGroups(groupname = "pncA", color = "#f0e662") %>%
          visGroups(groupname = "rpsA", color = "#f0e884") %>%
          
          visGroups(groupname = "gid", color = "#CC79A7") %>%
          visGroups(groupname = "rpsL", color = "#cc8baf") %>%
          visGroups(groupname = "rrs", color = "#c9a1b7") %>%
          visGroups(groupname = "tlyA", color = "#c9bbc3") %>%
          visGroups(groupname = "eis", color = "#c9c9c9") %>%
          
          visGroups(groupname = "gyrA", color = "#999999") %>%
          visGroups(groupname = "gyrB", color = "#7d7d7d") %>%
          
          visGroups(groupname = "rpoB_PPI", color = list(background= "#56B4E9", border="black")) %>%
          visGroups(groupname = "rpoC_PPI", color = list(background= "#0072B2", border="black")) %>%
          
          visGroups(groupname = "katG_PPI", color = list(background= "#D55E00", border="black")) %>%
          visGroups(groupname = "inhA_PPI", color = list(background= "#E69F00", border="black")) %>%
          visGroups(groupname = "ahpC_PPI", color = list(background= "#f2bf4e", border="black")) %>%
          visGroups(groupname = "kasA_PPI", color = list(background= "#ebc97f", border="black")) %>%
          visGroups(groupname = "fabG1_PPI", color = list(background= "#edd59f", border="black")) %>%
          
          visGroups(groupname = "embA_PPI", color = list(background= "#4da890", border="black")) %>%
          visGroups(groupname = "embB_PPI", color = list(background= "#009E73", border="black")) %>%
          visGroups(groupname = "embC_PPI", color = list(background= "#68ab99", border="black")) %>%
          visGroups(groupname = "embR_PPI", color = list(background= "#84ada2", border="black")) %>%
          
          visGroups(groupname = "panD_PPI", color = list(background= "#F0E442", border="black")) %>%
          visGroups(groupname = "pncA_PPI", color = list(background= "#f0e662", border="black")) %>%
          visGroups(groupname = "rpsA_PPI", color = list(background= "#f0e884", border="black")) %>%
          
          visGroups(groupname = "gid_PPI", color = list(background= "#CC79A7", border="black")) %>%
          visGroups(groupname = "rpsL_PPI", color = list(background= "#cc8baf", border="black")) %>%
          visGroups(groupname = "rrs_PPI", color = list(background= "#c9a1b7", border="black")) %>%
          visGroups(groupname = "tlyA_PPI", color = list(background= "#c9bbc3", border="black")) %>%
          visGroups(groupname = "eis_PPI", color = list(background= "#c9c9c9", border="black")) %>%
          
          visGroups(groupname = "gyrA_PPI", color = list(background= "#999999", border="black")) %>%
          visGroups(groupname = "gyrB_PPI", color = list(background= "#7d7d7d", border="black")) %>%
          
          visLegend(addNodes = list(list(label="rpoB",shape="dot",size=10,color="#56B4E9",font=list(color="black", size=10)),
                                    list(label="rpoC",shape="dot",size=10,color="#0072B2",font=list(color="black", size=10)),
                                    list(label="katG",shape="dot",size=10,color="#D55E00",font=list(color="black", size=10)),
                                    list(label="inhA",shape="dot",size=10,color="#E69F00",font=list(color="black", size=10)),
                                    list(label="ahpC",shape="dot",size=10,color="#f2bf4e",font=list(color="black", size=10)),
                                    list(label="kasA",shape="dot",size=10,color="#ebc97f",font=list(color="black", size=10)),
                                    list(label="fabG1",shape="dot",size=10,color="#edd59f",font=list(color="black", size=10)),
                                    list(label="embA",shape="dot",size=10,color="#4da890",font=list(color="black", size=10)),
                                    list(label="embB",shape="dot",size=10,color="#009E73",font=list(color="black", size=10)),
                                    list(label="embC",shape="dot",size=10,color="#68ab99",font=list(color="black", size=10)),
                                    list(label="embR",shape="dot",size=10,color="#84ada2",font=list(color="black", size=10)),
                                    list(label="panD",shape="dot",size=10,color="#F0E442",font=list(color="black", size=10)),
                                    list(label="pncA",shape="dot",size=10,color="#f0e662",font=list(color="black", size=10)),
                                    list(label="rpsA",shape="dot",size=10,color="#f0e884",font=list(color="black", size=10)),
                                    list(label="gid",shape="dot",size=10,color="#CC79A7",font=list(color="black", size=10)),
                                    list(label="rpsL",shape="dot",size=10,color="#cc8baf",font=list(color="black", size=10)),
                                    list(label="rrs",shape="dot",size=10,color="#c9a1b7",font=list(color="black", size=10)),
                                    list(label="tlyA",shape="dot",size=10,color="#c9bbc3",font=list(color="black", size=10)),
                                    list(label="eis",shape="dot",size=10,color="#c9c9c9",font=list(color="black", size=10)),
                                    list(label="gyrA",shape="dot",size=10,color="#999999",font=list(color="black", size=10)),
                                    list(label="gyrB",shape="dot",size=10,color="#7d7d7d",font=list(color="black", size=10)))
                    ,
                    useGroups = FALSE, ncol=3)  %>%
          visNodes(font = list(size = 25) , 
                   scaling = list(label = list(
                     enabled = TRUE, 
                     min = 25, max = 100, 
                     maxVisible = 100, 
                     drawThreshold = 1
                   )))
        if (input$layout=="Default"){
          plot2 <- plot1 %>%
            visIgraphLayout(randomSeed = 10)
        } else {
          plot2 <- plot1 %>%
            visIgraphLayout(layout = "layout_on_sphere", randomSeed = 10)
        }
        return(plot2)
      })
    }
  })
  
}


shinyApp(ui = ui, server = server)




```

## Embedded Application

It's also possible to embed an entire Shiny application within an R Markdown document using the `shinyAppDir` function. This example embeds a Shiny application located in another directory:

```{r tabsets, echo=FALSE}
shinyAppDir(
  system.file("examples/06_tabsets", package = "shiny"),
  options = list(
    width = "100%", height = 550
  )
)
```

Note the use of the `height` parameter to determine how much vertical space the embedded application should occupy.

You can also use the `shinyApp` function to define an application inline rather then in an external directory.

In all of R code chunks above the `echo = FALSE` attribute is used. This is to prevent the R code within the chunk from rendering in the document alongside the Shiny components.



