---
title: "Interactive Knowledge Graphs: First-line drugs (RIF and INH)"
author: "N Billows"
output: html_document
runtime: shiny
css: temp.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(dplyr,quietly = TRUE)
library(visNetwork, quietly = TRUE)
library(shiny,quietly = TRUE)
library(igraph, quietly = TRUE)
set.seed(10)
```

## Interactive Knowledge Graphs: First-line drugs (RIF and INH)
- The following presentation contains interactive knowledge graphs to explore feature interactions that occur in multi-label feature weighted random forest (ML-FWRF) prediction of drug-resistant phenotypes. 
- Features are classified into known drug-resistance mutations, co-occurring mutations and lineage-specific mutations according to the TB-Profiler database and predefined lineage barcodes.
- Interaction coefficients are used to construct networks and domain knowledge is integrated to build knowledge graphs for explainable and interpretable machine learning prediction. 
- Analysis was originally performed using a pipeline, for the purpose of this presentation, code is repeated for each drug.


## Rifampicin

```{r Rifampicin}
nodes_rifampicin <- read.csv("nodes_rifampicin.csv", header=TRUE)
edges_rifampicin <- read.csv("edges_rifampicin.csv", header=TRUE)
drug_name <- "rifampicin"
#User interface for Shiny and Visnetwork
ui <- fluidPage(title = "example",
                fillPage(sidebarLayout(
                  sidebarPanel(
                    selectInput(
                      inputId = "filterNodes",
                      label = "Filter nodes in candidate genes:",
                      choices = c("Yes", "No"),
                      selected = c("No")
                    ), 
                    checkboxGroupInput(
                      inputId = "filterEdges",
                      label = paste0("Role in ", drug_name, " resistance:"),
                      choices = unique(edges_rifampicin$knowledge_score),
                      selected = c("Likely", "Highly likely", "Not Applicable","Unlikely", "Highly unlikely")
                    )
                    ,
                    selectInput(
                      inputId = "filterEdges2",
                      label = "Show strong interactions only:",
                      choices = c("Yes", "No"),
                      selected = c("No")
                    ),
                    checkboxGroupInput(
                      inputId = "filterNodes2",
                      label = "Confers:",
                      choices = unique(nodes_rifampicin$type),
                      selected = unique(nodes_rifampicin$type)
                    ),
                    selectInput(
                      inputId = "filterNodes3",
                      label = "Hide PPI network:",
                      choices = c("Yes", "No"),
                      selected = c("No")
                    ),
                    selectInput(
                      inputId = "layout",
                      label = "Layout:",
                      choices = c("Default", "Circle"),
                      selected = c("Default")
                    )
                    ,
                    width = 3
                  ),
                  mainPanel(
                    visNetworkOutput("network_proxy_update", width = "100%", height = "90vh"),  
                    width = 9
                  )
                )))


nodes_rifampicin$font.size <- 30

#Server
server <- function(input, output) {
  output$network_proxy_update <- renderVisNetwork({
    visNetwork(nodes_rifampicin, edges_rifampicin) %>%  visIgraphLayout(randomSeed = 10) %>%
      visGroups(groupname = "rpoB", color = "#56B4E9") %>%
      visGroups(groupname = "rpoC", color = "#0072B2") %>%
      
      visGroups(groupname = "katG", color = "#D55E00") %>%
      visGroups(groupname = "inhA", color = "#E69F00") %>%
      visGroups(groupname = "ahpC", color = "#f2bf4e") %>%
      visGroups(groupname = "kasA", color = "#ebc97f") %>%
      visGroups(groupname = "fabG1", color = "#edd59f") %>%
      
      visGroups(groupname = "embA", color = "#4da890") %>%
      visGroups(groupname = "embB", color = "#009E73") %>%
      visGroups(groupname = "embC", color = "#68ab99") %>%
      visGroups(groupname = "embR", color = "#84ada2") %>%
      
      visGroups(groupname = "panD", color = "#F0E442") %>%
      visGroups(groupname = "pncA", color = "#f0e662") %>%
      visGroups(groupname = "rpsA", color = "#f0e884") %>%
      
      visGroups(groupname = "gid", color = "#CC79A7") %>%
      visGroups(groupname = "rpsL", color = "#cc8baf") %>%
      visGroups(groupname = "rrs", color = "#c9a1b7") %>%
      visGroups(groupname = "tlyA", color = "#c9bbc3") %>%
      visGroups(groupname = "eis", color = "#c9c9c9") %>%
      
      visGroups(groupname = "gyrA", color = "#999999") %>%
      visGroups(groupname = "gyrB", color = "#7d7d7d") %>%
      
      visGroups(groupname = "rpoB_PPI", color =  "#56B4E9") %>%
      visGroups(groupname = "rpoC_PPI", color =  "#0072B2") %>%
      
      visGroups(groupname = "katG_PPI", color =  "#D55E00") %>%
      visGroups(groupname = "inhA_PPI", color =  "#E69F00") %>%
      visGroups(groupname = "ahpC_PPI", color =  "#f2bf4e") %>%
      visGroups(groupname = "kasA_PPI", color =  "#ebc97f") %>%
      visGroups(groupname = "fabG1_PPI", color =  "#edd59f") %>%
      
      visGroups(groupname = "embA_PPI", color =  "#4da890") %>%
      visGroups(groupname = "embB_PPI", color =  "#009E73") %>%
      visGroups(groupname = "embC_PPI", color =  "#68ab99") %>%
      visGroups(groupname = "embR_PPI", color =  "#84ada2") %>%
      
      visGroups(groupname = "panD_PPI", color =  "#F0E442") %>%
      visGroups(groupname = "pncA_PPI", color =  "#f0e662") %>%
      visGroups(groupname = "rpsA_PPI", color =  "#f0e884") %>%
      
      visGroups(groupname = "gid_PPI", color =  "#CC79A7") %>%
      visGroups(groupname = "rpsL_PPI", color =  "#cc8baf") %>%
      visGroups(groupname = "rrs_PPI", color =  "#c9a1b7") %>%
      visGroups(groupname = "tlyA_PPI", color =  "#c9bbc3") %>%
      visGroups(groupname = "eis_PPI", color =  "#c9c9c9") %>%
      
      visGroups(groupname = "gyrA_PPI", color =  "#999999") %>%
      visGroups(groupname = "gyrB_PPI", color =  "#7d7d7d") %>%
      
      visLegend(addNodes = list(list(label="rpoB",shape="dot",size=10,color="#56B4E9",font=list(color="black", size=10)),
                                list(label="rpoC",shape="dot",size=10,color="#0072B2",font=list(color="black", size=10)),
                                list(label="katG",shape="dot",size=10,color="#D55E00",font=list(color="black", size=10)),
                                list(label="inhA",shape="dot",size=10,color="#E69F00",font=list(color="black", size=10)),
                                list(label="ahpC",shape="dot",size=10,color="#f2bf4e",font=list(color="black", size=10)),
                                list(label="kasA",shape="dot",size=10,color="#ebc97f",font=list(color="black", size=10)),
                                list(label="fabG1",shape="dot",size=10,color="#edd59f",font=list(color="black", size=10)),
                                list(label="embA",shape="dot",size=10,color="#4da890",font=list(color="black", size=10)),
                                list(label="embB",shape="dot",size=10,color="#009E73",font=list(color="black", size=10)),
                                list(label="embC",shape="dot",size=10,color="#68ab99",font=list(color="black", size=10)),
                                list(label="embR",shape="dot",size=10,color="#84ada2",font=list(color="black", size=10)),
                                list(label="panD",shape="dot",size=10,color="#F0E442",font=list(color="black", size=10)),
                                list(label="pncA",shape="dot",size=10,color="#f0e662",font=list(color="black", size=10)),
                                list(label="rpsA",shape="dot",size=10,color="#f0e884",font=list(color="black", size=10)),
                                list(label="gid",shape="dot",size=10,color="#CC79A7",font=list(color="black", size=10)),
                                list(label="rpsL",shape="dot",size=10,color="#cc8baf",font=list(color="black", size=10)),
                                list(label="rrs",shape="dot",size=10,color="#c9a1b7",font=list(color="black", size=10)),
                                list(label="tlyA",shape="dot",size=10,color="#c9bbc3",font=list(color="black", size=10)),
                                list(label="eis",shape="dot",size=10,color="#c9c9c9",font=list(color="black", size=10)),
                                list(label="gyrA",shape="dot",size=10,color="#999999",font=list(color="black", size=10)),
                                list(label="gyrB",shape="dot",size=10,color="#7d7d7d",font=list(color="black", size=10)))
                ,
                useGroups = FALSE, ncol=3) %>% 
      visNodes(font = list(size = 25) , 
               scaling = list(label = list(
                 enabled = TRUE, 
                 min = 25, max = 100, 
                 maxVisible = 100, 
                 drawThreshold = 1
               )))
  })
  myVisNetworkProxy <- visNetworkProxy("network_proxy_update") 
  observe ({
    myfilteredEdges <- edges_rifampicin %>% filter(knowledge_score %in% input$filterEdges) %>% filter(if ("Yes" %in% input$filterEdges2){
      coeff2 %in% c("Yes")
    } else {
      coeff2 %in% unique(coeff2) 
    })                                                                                    
    
    myfilteredNodes <- nodes_rifampicin %>% filter(if ("Yes" %in% input$filterNodes){
      candgene %in% c(1)
    } else {
      candgene %in% c(0,1)      
    }) %>% 
      filter(id %in% c(myfilteredEdges$to, myfilteredEdges$from)) %>% filter(type %in% input$filterNodes2)  %>% 
      filter(if ("Yes" %in% input$filterNodes3){
        !id %in% unique(nodes_rifampicin$gene)
      } else {
        id %in% id
      })
    myhiddenEdges <- anti_join(edges_rifampicin, myfilteredEdges)
    myhiddenNodes <- anti_join(nodes_rifampicin, myfilteredNodes)
    visRemoveEdges(myVisNetworkProxy, id = myhiddenEdges$name)
    visRemoveNodes(myVisNetworkProxy, id = myhiddenNodes$id)
    visUpdateEdges(myVisNetworkProxy, myfilteredEdges)
    visUpdateNodes(myVisNetworkProxy, nodes = myfilteredNodes)
    if (nrow(myfilteredNodes)<200){
      output$network_proxy_update <- renderVisNetwork({
        plot1 <- visNetwork(myfilteredNodes, myfilteredEdges) %>%  
          visGroups(groupname = "rpoB", color = "#56B4E9") %>%
          visGroups(groupname = "rpoC", color = "#0072B2") %>%
          
          visGroups(groupname = "katG", color = "#D55E00") %>%
          visGroups(groupname = "inhA", color = "#E69F00") %>%
          visGroups(groupname = "ahpC", color = "#f2bf4e") %>%
          visGroups(groupname = "kasA", color = "#ebc97f") %>%
          visGroups(groupname = "fabG1", color = "#edd59f") %>%
          
          visGroups(groupname = "embA", color = "#4da890") %>%
          visGroups(groupname = "embB", color = "#009E73") %>%
          visGroups(groupname = "embC", color = "#68ab99") %>%
          visGroups(groupname = "embR", color = "#84ada2") %>%
          
          visGroups(groupname = "panD", color = "#F0E442") %>%
          visGroups(groupname = "pncA", color = "#f0e662") %>%
          visGroups(groupname = "rpsA", color = "#f0e884") %>%
          
          visGroups(groupname = "gid", color = "#CC79A7") %>%
          visGroups(groupname = "rpsL", color = "#cc8baf") %>%
          visGroups(groupname = "rrs", color = "#c9a1b7") %>%
          visGroups(groupname = "tlyA", color = "#c9bbc3") %>%
          visGroups(groupname = "eis", color = "#c9c9c9") %>%
          
          visGroups(groupname = "gyrA", color = "#999999") %>%
          visGroups(groupname = "gyrB", color = "#7d7d7d") %>%
          
          visGroups(groupname = "rpoB_PPI", color = list(background= "#56B4E9", border="black")) %>%
          visGroups(groupname = "rpoC_PPI", color = list(background= "#0072B2", border="black")) %>%
          
          visGroups(groupname = "katG_PPI", color = list(background= "#D55E00", border="black")) %>%
          visGroups(groupname = "inhA_PPI", color = list(background= "#E69F00", border="black")) %>%
          visGroups(groupname = "ahpC_PPI", color = list(background= "#f2bf4e", border="black")) %>%
          visGroups(groupname = "kasA_PPI", color = list(background= "#ebc97f", border="black")) %>%
          visGroups(groupname = "fabG1_PPI", color = list(background= "#edd59f", border="black")) %>%
          
          visGroups(groupname = "embA_PPI", color = list(background= "#4da890", border="black")) %>%
          visGroups(groupname = "embB_PPI", color = list(background= "#009E73", border="black")) %>%
          visGroups(groupname = "embC_PPI", color = list(background= "#68ab99", border="black")) %>%
          visGroups(groupname = "embR_PPI", color = list(background= "#84ada2", border="black")) %>%
          
          visGroups(groupname = "panD_PPI", color = list(background= "#F0E442", border="black")) %>%
          visGroups(groupname = "pncA_PPI", color = list(background= "#f0e662", border="black")) %>%
          visGroups(groupname = "rpsA_PPI", color = list(background= "#f0e884", border="black")) %>%
          
          visGroups(groupname = "gid_PPI", color = list(background= "#CC79A7", border="black")) %>%
          visGroups(groupname = "rpsL_PPI", color = list(background= "#cc8baf", border="black")) %>%
          visGroups(groupname = "rrs_PPI", color = list(background= "#c9a1b7", border="black")) %>%
          visGroups(groupname = "tlyA_PPI", color = list(background= "#c9bbc3", border="black")) %>%
          visGroups(groupname = "eis_PPI", color = list(background= "#c9c9c9", border="black")) %>%
          
          visGroups(groupname = "gyrA_PPI", color = list(background= "#999999", border="black")) %>%
          visGroups(groupname = "gyrB_PPI", color = list(background= "#7d7d7d", border="black")) %>%
          
          visGroups(groupname = "ofloxacin", color = "#999999") %>%
          visGroups(groupname = "moxifloxacin", color = "#7d7d7d") %>%
          visGroups(groupname = "streptomycin", color = "#CC79A7") %>%
          visGroups(groupname = "amikacin", color = "#c9a1b7") %>%
          visGroups(groupname = "capreomycin", color = "#c9bbc3") %>%
          visGroups(groupname = "kanamycin", color = "#c9c9c9") %>%
          visGroups(groupname = "pyrazinamide", color = "#f0e662") %>%
          visGroups(groupname = "ethambutol", color = "#009E73") %>%
          visGroups(groupname = "isoniazid", color = "#D55E00") %>%
          visGroups(groupname = "rifampicin", color = "#56B4E9") %>%
          
          visLegend(addNodes = list(list(label="rpoB",shape="dot",size=10,color="#56B4E9",font=list(color="black", size=10)),
                                    list(label="rpoC",shape="dot",size=10,color="#0072B2",font=list(color="black", size=10)),
                                    list(label="katG",shape="dot",size=10,color="#D55E00",font=list(color="black", size=10)),
                                    list(label="inhA",shape="dot",size=10,color="#E69F00",font=list(color="black", size=10)),
                                    list(label="ahpC",shape="dot",size=10,color="#f2bf4e",font=list(color="black", size=10)),
                                    list(label="kasA",shape="dot",size=10,color="#ebc97f",font=list(color="black", size=10)),
                                    list(label="fabG1",shape="dot",size=10,color="#edd59f",font=list(color="black", size=10)),
                                    list(label="embA",shape="dot",size=10,color="#4da890",font=list(color="black", size=10)),
                                    list(label="embB",shape="dot",size=10,color="#009E73",font=list(color="black", size=10)),
                                    list(label="embC",shape="dot",size=10,color="#68ab99",font=list(color="black", size=10)),
                                    list(label="embR",shape="dot",size=10,color="#84ada2",font=list(color="black", size=10)),
                                    list(label="panD",shape="dot",size=10,color="#F0E442",font=list(color="black", size=10)),
                                    list(label="pncA",shape="dot",size=10,color="#f0e662",font=list(color="black", size=10)),
                                    list(label="rpsA",shape="dot",size=10,color="#f0e884",font=list(color="black", size=10)),
                                    list(label="gid",shape="dot",size=10,color="#CC79A7",font=list(color="black", size=10)),
                                    list(label="rpsL",shape="dot",size=10,color="#cc8baf",font=list(color="black", size=10)),
                                    list(label="rrs",shape="dot",size=10,color="#c9a1b7",font=list(color="black", size=10)),
                                    list(label="tlyA",shape="dot",size=10,color="#c9bbc3",font=list(color="black", size=10)),
                                    list(label="eis",shape="dot",size=10,color="#c9c9c9",font=list(color="black", size=10)),
                                    list(label="gyrA",shape="dot",size=10,color="#999999",font=list(color="black", size=10)),
                                    list(label="gyrB",shape="dot",size=10,color="#7d7d7d",font=list(color="black", size=10)))
                    ,
                    useGroups = FALSE, ncol=3)  %>%
          visNodes(font = list(size = 25) , 
                   scaling = list(label = list(
                     enabled = TRUE, 
                     min = 25, max = 100, 
                     maxVisible = 100, 
                     drawThreshold = 1
                   )))
        if (input$layout=="Default"){
          plot2 <- plot1 %>%
            visIgraphLayout(randomSeed = 10)
        } else {
          plot2 <- plot1 %>%
            visIgraphLayout(layout = "layout_on_sphere", randomSeed = 10)
        }
        return(plot2)
      })
    }
  })
  
}

#Make interactive network
shinyApp(ui = ui, server = server)

```

## Isoniazid

```{r Isoniazid}
nodes_isoniazid<- read.csv("nodes_isoniazid.csv", header=TRUE)
edges_isoniazid <- read.csv("edges_isoniazid.csv", header=TRUE)
drug_name <- "isoniazid"
#User interface for Shiny and Visnetwork
ui <- fluidPage(title = "example",
                fillPage(sidebarLayout(
                  sidebarPanel(
                    selectInput(
                      inputId = "filterNodes",
                      label = "Filter nodes in candidate genes:",
                      choices = c("Yes", "No"),
                      selected = c("No")
                    ), 
                    checkboxGroupInput(
                      inputId = "filterEdges",
                      label = paste0("Role in ", drug_name, " resistance:"),
                      choices = unique(edges_isoniazid$knowledge_score),
                      selected = c("Likely", "Highly likely", "Not Applicable","Unlikely", "Highly unlikely")
                    )
                    ,
                    selectInput(
                      inputId = "filterEdges2",
                      label = "Show strong interactions only:",
                      choices = c("Yes", "No"),
                      selected = c("No")
                    ),
                    checkboxGroupInput(
                      inputId = "filterNodes2",
                      label = "Confers:",
                      choices = unique(nodes_isoniazid$type),
                      selected = unique(nodes_isoniazid$type)
                    ),
                    selectInput(
                      inputId = "filterNodes3",
                      label = "Hide PPI network:",
                      choices = c("Yes", "No"),
                      selected = c("No")
                    ),
                    selectInput(
                      inputId = "layout",
                      label = "Layout:",
                      choices = c("Default", "Circle"),
                      selected = c("Default")
                    )
                    ,
                    width = 3
                  ),
                  mainPanel(
                    visNetworkOutput("network_proxy_update", width = "100%", height = "90vh"),  
                    width = 9
                  )
                )))


nodes_isoniazid$font.size <- 30

#Server
server <- function(input, output) {
  output$network_proxy_update <- renderVisNetwork({
    visNetwork(nodes_isoniazid, edges_isoniazid) %>%  visIgraphLayout(randomSeed = 10) %>%
      visGroups(groupname = "rpoB", color = "#56B4E9") %>%
      visGroups(groupname = "rpoC", color = "#0072B2") %>%
      
      visGroups(groupname = "katG", color = "#D55E00") %>%
      visGroups(groupname = "inhA", color = "#E69F00") %>%
      visGroups(groupname = "ahpC", color = "#f2bf4e") %>%
      visGroups(groupname = "kasA", color = "#ebc97f") %>%
      visGroups(groupname = "fabG1", color = "#edd59f") %>%
      
      visGroups(groupname = "embA", color = "#4da890") %>%
      visGroups(groupname = "embB", color = "#009E73") %>%
      visGroups(groupname = "embC", color = "#68ab99") %>%
      visGroups(groupname = "embR", color = "#84ada2") %>%
      
      visGroups(groupname = "panD", color = "#F0E442") %>%
      visGroups(groupname = "pncA", color = "#f0e662") %>%
      visGroups(groupname = "rpsA", color = "#f0e884") %>%
      
      visGroups(groupname = "gid", color = "#CC79A7") %>%
      visGroups(groupname = "rpsL", color = "#cc8baf") %>%
      visGroups(groupname = "rrs", color = "#c9a1b7") %>%
      visGroups(groupname = "tlyA", color = "#c9bbc3") %>%
      visGroups(groupname = "eis", color = "#c9c9c9") %>%
      
      visGroups(groupname = "gyrA", color = "#999999") %>%
      visGroups(groupname = "gyrB", color = "#7d7d7d") %>%
      
      visGroups(groupname = "rpoB_PPI", color =  "#56B4E9") %>%
      visGroups(groupname = "rpoC_PPI", color =  "#0072B2") %>%
      
      visGroups(groupname = "katG_PPI", color =  "#D55E00") %>%
      visGroups(groupname = "inhA_PPI", color =  "#E69F00") %>%
      visGroups(groupname = "ahpC_PPI", color =  "#f2bf4e") %>%
      visGroups(groupname = "kasA_PPI", color =  "#ebc97f") %>%
      visGroups(groupname = "fabG1_PPI", color =  "#edd59f") %>%
      
      visGroups(groupname = "embA_PPI", color =  "#4da890") %>%
      visGroups(groupname = "embB_PPI", color =  "#009E73") %>%
      visGroups(groupname = "embC_PPI", color =  "#68ab99") %>%
      visGroups(groupname = "embR_PPI", color =  "#84ada2") %>%
      
      visGroups(groupname = "panD_PPI", color =  "#F0E442") %>%
      visGroups(groupname = "pncA_PPI", color =  "#f0e662") %>%
      visGroups(groupname = "rpsA_PPI", color =  "#f0e884") %>%
      
      visGroups(groupname = "gid_PPI", color =  "#CC79A7") %>%
      visGroups(groupname = "rpsL_PPI", color =  "#cc8baf") %>%
      visGroups(groupname = "rrs_PPI", color =  "#c9a1b7") %>%
      visGroups(groupname = "tlyA_PPI", color =  "#c9bbc3") %>%
      visGroups(groupname = "eis_PPI", color =  "#c9c9c9") %>%
      
      visGroups(groupname = "gyrA_PPI", color =  "#999999") %>%
      visGroups(groupname = "gyrB_PPI", color =  "#7d7d7d") %>%
      
      visLegend(addNodes = list(list(label="rpoB",shape="dot",size=10,color="#56B4E9",font=list(color="black", size=10)),
                                list(label="rpoC",shape="dot",size=10,color="#0072B2",font=list(color="black", size=10)),
                                list(label="katG",shape="dot",size=10,color="#D55E00",font=list(color="black", size=10)),
                                list(label="inhA",shape="dot",size=10,color="#E69F00",font=list(color="black", size=10)),
                                list(label="ahpC",shape="dot",size=10,color="#f2bf4e",font=list(color="black", size=10)),
                                list(label="kasA",shape="dot",size=10,color="#ebc97f",font=list(color="black", size=10)),
                                list(label="fabG1",shape="dot",size=10,color="#edd59f",font=list(color="black", size=10)),
                                list(label="embA",shape="dot",size=10,color="#4da890",font=list(color="black", size=10)),
                                list(label="embB",shape="dot",size=10,color="#009E73",font=list(color="black", size=10)),
                                list(label="embC",shape="dot",size=10,color="#68ab99",font=list(color="black", size=10)),
                                list(label="embR",shape="dot",size=10,color="#84ada2",font=list(color="black", size=10)),
                                list(label="panD",shape="dot",size=10,color="#F0E442",font=list(color="black", size=10)),
                                list(label="pncA",shape="dot",size=10,color="#f0e662",font=list(color="black", size=10)),
                                list(label="rpsA",shape="dot",size=10,color="#f0e884",font=list(color="black", size=10)),
                                list(label="gid",shape="dot",size=10,color="#CC79A7",font=list(color="black", size=10)),
                                list(label="rpsL",shape="dot",size=10,color="#cc8baf",font=list(color="black", size=10)),
                                list(label="rrs",shape="dot",size=10,color="#c9a1b7",font=list(color="black", size=10)),
                                list(label="tlyA",shape="dot",size=10,color="#c9bbc3",font=list(color="black", size=10)),
                                list(label="eis",shape="dot",size=10,color="#c9c9c9",font=list(color="black", size=10)),
                                list(label="gyrA",shape="dot",size=10,color="#999999",font=list(color="black", size=10)),
                                list(label="gyrB",shape="dot",size=10,color="#7d7d7d",font=list(color="black", size=10)))
                ,
                useGroups = FALSE, ncol=3) %>% 
      visNodes(font = list(size = 25) , 
               scaling = list(label = list(
                 enabled = TRUE, 
                 min = 25, max = 100, 
                 maxVisible = 100, 
                 drawThreshold = 1
               )))
  })
  myVisNetworkProxy <- visNetworkProxy("network_proxy_update") 
  observe ({
    myfilteredEdges <- edges_isoniazid %>% filter(knowledge_score %in% input$filterEdges) %>% filter(if ("Yes" %in% input$filterEdges2){
      coeff2 %in% c("Yes")
    } else {
      coeff2 %in% unique(coeff2) 
    })                                                                                    
    
    myfilteredNodes <- nodes_isoniazid %>% filter(if ("Yes" %in% input$filterNodes){
      candgene %in% c(1)
    } else {
      candgene %in% c(0,1)      
    }) %>% 
      filter(id %in% c(myfilteredEdges$to, myfilteredEdges$from)) %>% filter(type %in% input$filterNodes2)  %>% 
      filter(if ("Yes" %in% input$filterNodes3){
        !id %in% unique(nodes_isoniazid$gene)
      } else {
        id %in% id
      })
    myhiddenEdges <- anti_join(edges_isoniazid, myfilteredEdges)
    myhiddenNodes <- anti_join(nodes_isoniazid, myfilteredNodes)
    visRemoveEdges(myVisNetworkProxy, id = myhiddenEdges$name)
    visRemoveNodes(myVisNetworkProxy, id = myhiddenNodes$id)
    visUpdateEdges(myVisNetworkProxy, myfilteredEdges)
    visUpdateNodes(myVisNetworkProxy, nodes = myfilteredNodes)
    if (nrow(myfilteredNodes)<200){
      output$network_proxy_update <- renderVisNetwork({
        plot1 <- visNetwork(myfilteredNodes, myfilteredEdges) %>%  
          visGroups(groupname = "rpoB", color = "#56B4E9") %>%
          visGroups(groupname = "rpoC", color = "#0072B2") %>%
          
          visGroups(groupname = "katG", color = "#D55E00") %>%
          visGroups(groupname = "inhA", color = "#E69F00") %>%
          visGroups(groupname = "ahpC", color = "#f2bf4e") %>%
          visGroups(groupname = "kasA", color = "#ebc97f") %>%
          visGroups(groupname = "fabG1", color = "#edd59f") %>%
          
          visGroups(groupname = "embA", color = "#4da890") %>%
          visGroups(groupname = "embB", color = "#009E73") %>%
          visGroups(groupname = "embC", color = "#68ab99") %>%
          visGroups(groupname = "embR", color = "#84ada2") %>%
          
          visGroups(groupname = "panD", color = "#F0E442") %>%
          visGroups(groupname = "pncA", color = "#f0e662") %>%
          visGroups(groupname = "rpsA", color = "#f0e884") %>%
          
          visGroups(groupname = "gid", color = "#CC79A7") %>%
          visGroups(groupname = "rpsL", color = "#cc8baf") %>%
          visGroups(groupname = "rrs", color = "#c9a1b7") %>%
          visGroups(groupname = "tlyA", color = "#c9bbc3") %>%
          visGroups(groupname = "eis", color = "#c9c9c9") %>%
          
          visGroups(groupname = "gyrA", color = "#999999") %>%
          visGroups(groupname = "gyrB", color = "#7d7d7d") %>%
          
          visGroups(groupname = "rpoB_PPI", color = list(background= "#56B4E9", border="black")) %>%
          visGroups(groupname = "rpoC_PPI", color = list(background= "#0072B2", border="black")) %>%
          
          visGroups(groupname = "katG_PPI", color = list(background= "#D55E00", border="black")) %>%
          visGroups(groupname = "inhA_PPI", color = list(background= "#E69F00", border="black")) %>%
          visGroups(groupname = "ahpC_PPI", color = list(background= "#f2bf4e", border="black")) %>%
          visGroups(groupname = "kasA_PPI", color = list(background= "#ebc97f", border="black")) %>%
          visGroups(groupname = "fabG1_PPI", color = list(background= "#edd59f", border="black")) %>%
          
          visGroups(groupname = "embA_PPI", color = list(background= "#4da890", border="black")) %>%
          visGroups(groupname = "embB_PPI", color = list(background= "#009E73", border="black")) %>%
          visGroups(groupname = "embC_PPI", color = list(background= "#68ab99", border="black")) %>%
          visGroups(groupname = "embR_PPI", color = list(background= "#84ada2", border="black")) %>%
          
          visGroups(groupname = "panD_PPI", color = list(background= "#F0E442", border="black")) %>%
          visGroups(groupname = "pncA_PPI", color = list(background= "#f0e662", border="black")) %>%
          visGroups(groupname = "rpsA_PPI", color = list(background= "#f0e884", border="black")) %>%
          
          visGroups(groupname = "gid_PPI", color = list(background= "#CC79A7", border="black")) %>%
          visGroups(groupname = "rpsL_PPI", color = list(background= "#cc8baf", border="black")) %>%
          visGroups(groupname = "rrs_PPI", color = list(background= "#c9a1b7", border="black")) %>%
          visGroups(groupname = "tlyA_PPI", color = list(background= "#c9bbc3", border="black")) %>%
          visGroups(groupname = "eis_PPI", color = list(background= "#c9c9c9", border="black")) %>%
          
          visGroups(groupname = "gyrA_PPI", color = list(background= "#999999", border="black")) %>%
          visGroups(groupname = "gyrB_PPI", color = list(background= "#7d7d7d", border="black")) %>%
          
          visGroups(groupname = "ofloxacin", color = "#999999") %>%
          visGroups(groupname = "moxifloxacin", color = "#7d7d7d") %>%
          visGroups(groupname = "streptomycin", color = "#CC79A7") %>%
          visGroups(groupname = "amikacin", color = "#c9a1b7") %>%
          visGroups(groupname = "capreomycin", color = "#c9bbc3") %>%
          visGroups(groupname = "kanamycin", color = "#c9c9c9") %>%
          visGroups(groupname = "pyrazinamide", color = "#f0e662") %>%
          visGroups(groupname = "ethambutol", color = "#009E73") %>%
          visGroups(groupname = "isoniazid", color = "#D55E00") %>%
          visGroups(groupname = "rifampicin", color = "#56B4E9") %>%
          
          visLegend(addNodes = list(list(label="rpoB",shape="dot",size=10,color="#56B4E9",font=list(color="black", size=10)),
                                    list(label="rpoC",shape="dot",size=10,color="#0072B2",font=list(color="black", size=10)),
                                    list(label="katG",shape="dot",size=10,color="#D55E00",font=list(color="black", size=10)),
                                    list(label="inhA",shape="dot",size=10,color="#E69F00",font=list(color="black", size=10)),
                                    list(label="ahpC",shape="dot",size=10,color="#f2bf4e",font=list(color="black", size=10)),
                                    list(label="kasA",shape="dot",size=10,color="#ebc97f",font=list(color="black", size=10)),
                                    list(label="fabG1",shape="dot",size=10,color="#edd59f",font=list(color="black", size=10)),
                                    list(label="embA",shape="dot",size=10,color="#4da890",font=list(color="black", size=10)),
                                    list(label="embB",shape="dot",size=10,color="#009E73",font=list(color="black", size=10)),
                                    list(label="embC",shape="dot",size=10,color="#68ab99",font=list(color="black", size=10)),
                                    list(label="embR",shape="dot",size=10,color="#84ada2",font=list(color="black", size=10)),
                                    list(label="panD",shape="dot",size=10,color="#F0E442",font=list(color="black", size=10)),
                                    list(label="pncA",shape="dot",size=10,color="#f0e662",font=list(color="black", size=10)),
                                    list(label="rpsA",shape="dot",size=10,color="#f0e884",font=list(color="black", size=10)),
                                    list(label="gid",shape="dot",size=10,color="#CC79A7",font=list(color="black", size=10)),
                                    list(label="rpsL",shape="dot",size=10,color="#cc8baf",font=list(color="black", size=10)),
                                    list(label="rrs",shape="dot",size=10,color="#c9a1b7",font=list(color="black", size=10)),
                                    list(label="tlyA",shape="dot",size=10,color="#c9bbc3",font=list(color="black", size=10)),
                                    list(label="eis",shape="dot",size=10,color="#c9c9c9",font=list(color="black", size=10)),
                                    list(label="gyrA",shape="dot",size=10,color="#999999",font=list(color="black", size=10)),
                                    list(label="gyrB",shape="dot",size=10,color="#7d7d7d",font=list(color="black", size=10)))
                    ,
                    useGroups = FALSE, ncol=3)  %>%
          visNodes(font = list(size = 25) , 
                   scaling = list(label = list(
                     enabled = TRUE, 
                     min = 25, max = 100, 
                     maxVisible = 100, 
                     drawThreshold = 1
                   )))
        if (input$layout=="Default"){
          plot2 <- plot1 %>%
            visIgraphLayout(randomSeed = 10)
        } else {
          plot2 <- plot1 %>%
            visIgraphLayout(layout = "layout_on_sphere", randomSeed = 10)
        }
        return(plot2)
      })
    }
  })
  
}

#Make interactive network
shinyApp(ui = ui, server = server)

```





